---
title: "HW6"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(modelr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)
```

## Problem 1

#### Read in and tidy data

```{r}
homicide_df = 
  read_csv("./data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest" ~ 0,
      disposition == "Closed by arrest" ~ 1
    )
  ) %>% 
  filter(victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```

#### Do this for one city...

```{r}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")

glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df, 
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = (exp(estimate) - 1.96 * std.error),
    CI_upper = (exp(estimate) + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```

#### Do this for all cities

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, 
                 ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = (exp(estimate) - 1.96 * std.error),
    CI_upper = (exp(estimate) + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI"))
```

#### Plot

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR))+
  geom_point()+
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper))+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

## Problem 2

#### Read in and tidy data

```{r}
baby_df = 
  read.csv("./data/birthweight.csv") %>% 
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace)
  )
  
any(is.na(baby_df))
```

The four categorical variables (sex of baby, race of father, race of mother, presence of malformation) have been converted from numeric to factor. There appears to be no missing data in this dataset.

#### Looking at my proposed model

```{r}
proposed_model = lm(bwt ~ blength + gaweeks + babysex + wtgain, data = baby_df)
broom::glance(proposed_model)
broom::tidy(proposed_model) %>% 
  select(-std.error, -statistic) %>% 
  knitr::kable(digits = 3)


baby_df %>% 
  add_predictions(proposed_model) %>% 
  add_residuals(proposed_model) %>% 
  ggplot(aes(x = pred, y = resid))+
  geom_point()

baby_df %>% 
  add_residuals(proposed_model) %>% 
  ggplot(aes(x = resid))+ 
  geom_density()
```

I thought it would be interesting to look at how sex of the baby and weight gain during pregnancy, in addition to the main effects of gestational weeks and length of baby at birth, would be related to the baby's birth weight. I know there are old wives' tales about how babies assigned male at birth tend to make women gain more weight in pregnancy, so I thought that it could be good to look into how each of these relate to birth weight.

The scatterplot with predictions and residuals shows a few outliers, so I did a density plot to check the distribution of the residuals. The distribution looks quite normal, but the tail is quite a bit longer in the positive direction.

#### Building models, calculating RMSEs for each model, and making violin plots

```{r}
main_effects_model = lm(bwt ~ blength + gaweeks, data = baby_df)
proposed_model = lm(bwt ~ babysex + gaweeks + wtgain, data = baby_df)
model_3 = lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex +
               bhead*blength*babysex, data = baby_df)


cv_df = 
  crossv_mc(baby_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )

cv_df = 
  cv_df %>% 
  mutate(
    main_effects_model = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    proposed_model= map(.x = train, ~ lm(bwt ~ babysex + gaweeks + wtgain, data = .x)),
    model_3 = map(.x = train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + 
                                    blength*babysex + bhead*blength*babysex, data = .x))
  ) %>% 
  mutate(
    rmse_main = map2_dbl(.x = main_effects_model, .y = test, ~rmse(model = .x, data = .y)),
    rmse_proposed = map2_dbl(.x = proposed_model, .y = test, ~rmse(model = .x, data = .y)),
    rmse_mod3 = map2_dbl(.x = model_3, .y = test, ~rmse(model = .x, data = .y))
  )

cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_violin()
```

Model 3 has by far the lowest RMSEs, which indicates that this is the best model to fit the data. My proposed model is by far the worst in terms of RMSEs, so I will not try to enter the job field of model building.


## Problem 3

#### Loading in data according to instructions in HW document.

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

#### I am going to get estimates for `r.squared` first.

```{r}
weather_model = lm(tmax ~ tmin, data = weather_df)


r_squared = 
  weather_df %>% 
  bootstrap(5000, id = "strap_number") %>% 
  mutate(
    models = map(.x = strap, ~lm(tmax ~ tmin, data = .x)), 
    results = map(models, broom::glance)
  ) %>% 
  select(strap_number, results) %>% 
  unnest(results) %>% 
  select(r.squared)

r_squared %>% 
  summarize(
    ci_lower = quantile(r.squared, 0.025),
    ci_upper = quantile(r.squared, 0.975)
  ) %>% 
  knitr::kable(digits = 3)

r_squared %>% 
  ggplot(aes(x = r.squared))+
  geom_density()

```

First, I produced 5000 `r.squared` estimates using bootstrapping. Then, I created a data frame with the 95% confidence interval for these estimates. Lastly, I modeled the values obtained in a density plot, which seems mostly normal. Based on the plot, the `r.squared` values appear to be centered around 0.91, with a 95% confidence interval of roughly 0.89-0.93. 

#### Next, I need to get the log of the product of beta 1 and beta 0.

```{r}
log = 
  weather_df %>% 
  bootstrap(5000, id = "strap_number") %>% 
  mutate(
    models = map(.x = strap, ~lm(tmax ~ tmin, data = .x)), 
    results = map(models, broom::tidy)
  ) %>% 
  select(strap_number, results) %>% 
  unnest(results) %>% 
  select(strap_number, term, estimate) %>% 
  pivot_wider(
               names_from = term,
               values_from = estimate
               ) %>% 
  janitor::clean_names() %>% 
  summarize(
    log_estimate = log(intercept*tmin)
  )

log %>% 
  summarize(
    ci_lower = quantile(log_estimate, 0.025),
    ci_upper = quantile(log_estimate, 0.975)
  ) %>% 
  knitr::kable(digits = 3)

log %>% 
  ggplot(aes(x = log_estimate))+ 
  geom_density()
```

First, I isolated the intercept (b0) and tmin (b1) values and calculated the log of the product of them. Then, I made a table of the 95% confidence interval across those values. Finally, I made a density plot of these log product values. This plot has a relatively normal distribution, with a longer left tail than right. The values seem to be centered around 2.2, with a 95% confidence interval of roughly 1.96-2.06.

